Randomization Examples using `nycflights13` `flights` data

### 2018-07-11 inst/doc/flights_examples.Rmd

@@

```{r}
Chisq_hat <- fli_small %>%
  chisq_stat(formula = origin ~ NULL)
null_distn <- fli_small %>%
  specify(response = origin) %>%
  hypothesize(null = "point", 
              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "Chisq")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = pull(Chisq_hat), color = "red")
null_distn %>%
  summarize(p_value = mean(stat >= pull(Chisq_hat))) %>%
  pull()
```

>>>>

This vignette is designed to show how to use the {infer} package with {dplyr} syntax. It does not show how to calculate observed statistics or p-values using the {infer} package. To see examples of these, check out the "Computation of observed statistics..." vignette instead.

@@

```{r}
Chisq_hat <- fli_small %>%
  specify(response = origin) %>%
  hypothesize(null = "point", 
              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
  calculate(stat = "Chisq")
null_distn <- fli_small %>%
  specify(response = origin) %>%
  hypothesize(null = "point", 
              p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "Chisq")
ggplot(null_distn, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = pull(Chisq_hat), color = "red")
null_distn %>%
  summarize(p_value = mean(stat >= pull(Chisq_hat))) %>%
  pull()
```
